Supplementary Materials

### 2020-09-01 analysis/analysis.Rmd
Some small edits to supp mat

```{r}
d_eeg %>% group_by(subject) %>% summarise(count = n()) %>% knitr::kable()
```

@@

```{r fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals.", cache=TRUE}

@@

filter(df, p == 0.95)

@@

d_disp_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_disp_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_disp_rot, aes(x = orientation, y = threshold, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p2
```

```{r}
p1 + p2

>>>>

```{r}
d_eeg %>% group_by(subject) %>% 
  summarise(count = n()) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

```{r fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals.", cache=TRUE, warning=FALSE}

@@

filter(df, p == 0.95) %>% knitr::kable() %>% kableExtra::kable_styling(full_width = F)

@@

d_disp_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_disp_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_disp_rot, aes(x = orientation, y = threshold, group = subject), alpha = 0.1, colour = "red") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p2
```

```{r rotations-replication, fig.cap="Red lines show empirical data, blue lines show the model fit."}
p1 + p2
```
